---
title: "flextable package"
subtitle: "a grammar to produce tabular reporting from R"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ['default', 'static/ardata-remark.css']
---

---

## Formats

.marker-writting[
Remember that any formatting function can be coupled with selectors !
]

<pre class = "nomtop nombottom">
<code class="r remark-code">flextable(x) %>%
  <em>any_format_function</em>(<strong>i = ~ ..., j = ~ ...</strong>)
</code></pre>

---

## Formats


.row[

.col-xs-12[

<pre class = "nomtop nombottom">
<code class="r remark-code">x <- head(quakes) %>% flextable() %>% theme_box()
</code></pre>

```{r, echo = FALSE}
x <- head(quakes) %>% flextable() %>% theme_box()
inside  <- fp_border(color = "gray")
outside <- fp_border(color = "orange", width = 2)
cell    <- fp_border(color = "red", style = "dotted", width = 3)
````

]

]

.row[

.col-xs-6[

<pre class = "nomtop nombottom">
<code class="r remark-code">x
</code></pre>

]

.col-xs-6[

```{r, echo = FALSE}
x
```

]

]

---

## Formats


.row[

.col-xs-12[

<pre class = "nomtop nombottom">
<code class="r remark-code">x <- head(quakes) %>% flextable() %>% theme_box()
</code></pre>

```{r, echo = FALSE}
x <- head(quakes) %>% flextable() %>% theme_box()
````

]

]

.row[

.col-xs-6[

<pre class = "nomtop nombottom">
<code class="r remark-code">x %>%
  <strong>bold</strong>(i = 2)
</code></pre>

]

.col-xs-6[

```{r, echo = FALSE}
x %>%
  bold(i = 2)
```

]

]

---

## Formats


.row[

.col-xs-12[

<pre class = "nomtop nombottom">
<code class="r remark-code">x <- head(quakes) %>% flextable() %>% theme_box()
</code></pre>

```{r, echo = FALSE}
x <- head(quakes) %>% flextable() %>% theme_box()
````

]

]

.row[

.col-xs-6[

<pre class = "nomtop nombottom">
<code class="r remark-code">x %>%
  <strong>bold</strong>(i = 2) %>%
  <strong>italic</strong>(i = 2)
</code></pre>

]

.col-xs-6[

```{r, echo = FALSE}
x %>%
  bold(i = 2) %>%
  italic(i = 2)
```

]

]

---

## Formats


.row[

.col-xs-12[

<pre class = "nomtop nombottom">
<code class="r remark-code">x <- head(quakes) %>% flextable() %>% theme_box()
</code></pre>

```{r, echo = FALSE}
x <- head(quakes) %>% flextable() %>% theme_box()
````

]

]

.row[

.col-xs-6[

<pre class = "nomtop nombottom">
<code class="r remark-code">x %>%
  <strong>bold</strong>(i = 2) %>%
  <strong>italic</strong>(i = 2) %>%
  <strong>font</strong>(i = 2, fontname = "Times")
</code></pre>

]

.col-xs-6[

```{r, echo = FALSE}
x %>%
  bold(i = 2) %>%
  italic(i = 2) %>%
  font(i = 2, fontname = "Times")
```

]

]


---

## Formats


.row[

.col-xs-12[

<pre class = "nomtop nombottom">
<code class="r remark-code">x <- head(quakes) %>% flextable() %>% theme_box()
</code></pre>

```{r, echo = FALSE}
x <- head(quakes) %>% flextable() %>% theme_box()
````

]

]

.row[

.col-xs-6[

<pre class = "nomtop nombottom">
<code class="r remark-code">x %>%
  <strong>bold</strong>(i = 2) %>%
  <strong>italic</strong>(i = 2) %>%
  <strong>font</strong>(i = 2, fontname = "Times") %>%
  <strong>fontsize</strong>(i = 2, size = 14)
</code></pre>

]

.col-xs-6[

```{r, echo = FALSE}
x %>%
  bold(i = 2) %>%
  italic(i = 2) %>%
  font(i = 2, fontname = "Times") %>%
  fontsize(i = 2, size = 14)
```

]

]

---

## Formats


.row[

.col-xs-12[

<pre class = "nomtop nombottom">
<code class="r remark-code">x <- head(quakes) %>% flextable() %>% theme_box()
</code></pre>

```{r, echo = FALSE}
x <- head(quakes) %>% flextable() %>% theme_box()
````

]

]

.row[

.col-xs-6[

<pre class = "nomtop nombottom">
<code class="r remark-code">x %>%
  <strong>bold</strong>(i = 2) %>%
  <strong>italic</strong>(i = 2) %>%
  <strong>font</strong>(i = 2, fontname = "Times") %>%
  <strong>fontsize</strong>(i = 2, size = 14) %>%
  <strong>color</strong>(i = 2, color = "red)
</code></pre>

]

.col-xs-6[

```{r, echo = FALSE}
x %>%
  bold(i = 2) %>%
  italic(i = 2) %>%
  font(i = 2, fontname = "Times") %>%
  fontsize(i = 2, size = 14) %>%
  color(i = 2, color = "red")
```

]

]

---

## Formats


.row[

.col-xs-12[

<pre class = "nomtop nombottom">
<code class="r remark-code">x <- head(quakes) %>% flextable() %>% theme_box()
</code></pre>

```{r, echo = FALSE}
x <- head(quakes) %>% flextable() %>% theme_box()
````

]

]

.row[

.col-xs-6[

<pre class = "nomtop nombottom">
<code class="r remark-code">x %>%
  <strong>bold</strong>(i = 2) %>%
  <strong>italic</strong>(i = 2) %>%
  <strong>font</strong>(i = 2, fontname = "Times") %>%
  <strong>fontsize</strong>(i = 2, size = 14) %>%
  <strong>color</strong>(i = 2, color = "red)
</code></pre>

<pre class = "nomtop nombottom">
<code class="r remark-code">inside  <- fp_border(color = "gray")
outside <- fp_border(color = "orange", 
             width = 2)
</code></pre>

]

.col-xs-6[

```{r, echo = FALSE}
x %>%
  bold(i = 2) %>%
  italic(i = 2) %>%
  font(i = 2, fontname = "Times") %>%
  fontsize(i = 2, size = 14) %>%
  color(i = 2, color = "red")
```

]

]


---

## Formats


.row[

.col-xs-12[

<pre class = "nomtop nombottom">
<code class="r remark-code">x <- head(quakes) %>% flextable() %>% theme_box()
</code></pre>

```{r, echo = FALSE}
x <- head(quakes) %>% flextable() %>% theme_box()
````

]

]

.row[

.col-xs-6[

<pre class = "nomtop nombottom">
<code class="r remark-code">x %>%
  <strong>bold</strong>(i = 2) %>%
  <strong>italic</strong>(i = 2) %>%
  <strong>font</strong>(i = 2, fontname = "Times") %>%
  <strong>fontsize</strong>(i = 2, size = 14) %>%
  <strong>color</strong>(i = 2, color = "red)
</code></pre>

<pre class = "nomtop nombottom">
<code class="r remark-code">inside  <- fp_border(color = "gray")
outside <- fp_border(color = "orange", 
             width = 2)
</code></pre>

<pre class = "nomtop nombottom">
<code class="r remark-code">x %>%
  <strong>border_outer</strong>(border = <em>outside</em>)
</code></pre>

]

.col-xs-6[

```{r, echo = FALSE}
x %>%
  bold(i = 2) %>%
  italic(i = 2) %>%
  font(i = 2, fontname = "Times") %>%
  fontsize(i = 2, size = 14) %>%
  color(i = 2, color = "red") %>%
  border_outer(border = outside)
```

]

]

---

## Formats


.row[

.col-xs-12[

<pre class = "nomtop nombottom">
<code class="r remark-code">x <- head(quakes) %>% flextable() %>% theme_box()
</code></pre>

```{r, echo = FALSE}
x <- head(quakes) %>% flextable() %>% theme_box()
````

]

]

.row[

.col-xs-6[

<pre class = "nomtop nombottom">
<code class="r remark-code">x %>%
  <strong>bold</strong>(i = 2) %>%
  <strong>italic</strong>(i = 2) %>%
  <strong>font</strong>(i = 2, fontname = "Times") %>%
  <strong>fontsize</strong>(i = 2, size = 14) %>%
  <strong>color</strong>(i = 2, color = "red)
</code></pre>

<pre class = "nomtop nombottom">
<code class="r remark-code">inside  <- fp_border(color = "gray")
outside <- fp_border(color = "orange", 
             width = 2)
</code></pre>

<pre class = "nomtop nombottom">
<code class="r remark-code">x %>%
  <strong>border_outer</strong>(border = <em>outside</em>) %>%
  <strong>border_inner</strong>(border = <em>inside</em>)
</code></pre>

]

.col-xs-6[

```{r, echo = FALSE}
x %>%
  bold(i = 2) %>%
  italic(i = 2) %>%
  font(i = 2, fontname = "Times") %>%
  fontsize(i = 2, size = 14) %>%
  color(i = 2, color = "red") %>%
  border_outer(border = outside) %>%
  border_inner(border = inside)
```

]

]

---

## Formats


.row[

.col-xs-12[

<pre class = "nomtop nombottom">
<code class="r remark-code">x <- head(quakes) %>% flextable() %>% theme_box()
</code></pre>

```{r, echo = FALSE}
x <- head(quakes) %>% flextable() %>% theme_box()
````

]

]

.row[

.col-xs-6[

<pre class = "nomtop nombottom">
<code class="r remark-code">x %>%
  <strong>bold</strong>(i = 2) %>%
  <strong>italic</strong>(i = 2) %>%
  <strong>font</strong>(i = 2, fontname = "Times") %>%
  <strong>fontsize</strong>(i = 2, size = 14) %>%
  <strong>color</strong>(i = 2, color = "red)
</code></pre>

<pre class = "nomtop nombottom">
<code class="r remark-code">inside  <- fp_border(color = "gray")
outside <- fp_border(color = "orange", 
             width = 2)
</code></pre>

<pre class = "nomtop nombottom">
<code class="r remark-code">x %>%
  <strong>border_outer</strong>(border = <em>outside</em>) %>%
  <strong>border_inner</strong>(border = <em>inside</em>) %>%
  <strong>bg</strong>(i = ~ mag > 5, j = ~ lat + long,
    bg = "#becde6")
</code></pre>

]

.col-xs-6[

```{r, echo = FALSE}
x %>%
  bold(i = 2) %>%
  italic(i = 2) %>%
  font(i = 2, fontname = "Times") %>%
  fontsize(i = 2, size = 14) %>%
  color(i = 2, color = "red") %>%
  border_outer(border = outside) %>%
  border_inner(border = inside) %>%
  bg(i = ~ mag > 5, j = ~ lat + long, bg = "#becde6")
```

]

]

---

## Formats


.row[

.col-xs-12[

<pre class = "nomtop nombottom">
<code class="r remark-code">x <- head(quakes) %>% flextable() %>% theme_box()
</code></pre>

```{r, echo = FALSE}
x <- head(quakes) %>% flextable() %>% theme_box()
````

]

]

.row[

.col-xs-6[

<pre class = "nomtop nombottom">
<code class="r remark-code">x %>%
  <strong>bold</strong>(i = 2) %>%
  <strong>italic</strong>(i = 2) %>%
  <strong>font</strong>(i = 2, fontname = "Times") %>%
  <strong>fontsize</strong>(i = 2, size = 14) %>%
  <strong>color</strong>(i = 2, color = "red)
</code></pre>

<pre class = "nomtop nombottom">
<code class="r remark-code">inside  <- fp_border(color = "gray")
outside <- fp_border(color = "orange", 
             width = 2)
</code></pre>

<pre class = "nomtop nombottom">
<code class="r remark-code">x %>%
  <strong>border_outer</strong>(border = <em>outside</em>) %>%
  <strong>border_inner</strong>(border = <em>inside</em>) %>%
  <strong>bg</strong>(i = ~ mag > 5, j = ~ lat + long,
    bg = "#becde6")
</code></pre>

]

.col-xs-6[

```{r, echo = FALSE}
x %>%
  bold(i = 2) %>%
  italic(i = 2) %>%
  font(i = 2, fontname = "Times") %>%
  fontsize(i = 2, size = 14) %>%
  color(i = 2, color = "red") %>%
  border_outer(border = outside) %>%
  border_inner(border = inside) %>%
  bg(i = ~ mag > 5, j = ~ lat + long, bg = "#becde6")
```

]

]

.marker-writting[
Others formatting functions : align, padding, rotate, etc...
]