---
title: "flextable package"
subtitle: "a grammar to produce tabular reporting from R"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ['default', 'static/ardata-remark.css']
---

````{r, eval = TRUE, echo = FALSE}
library(flextable)
library(magrittr)
library(officer)
````

---

## Selectors


.row[

.col-xs-6[

.marker-writting[
You can select row(s), column(s) or cell(s) of any part to modify its :

* content
* layout
* format

]
]
]

---

## Selectors


.row[

.col-xs-6[

.marker-writting[
You can select row(s), column(s) or cell(s) of any part to modify its :

* content
* layout
* format

]
]
]

.row[

.col-xs-6[

<pre>
<code class="r hljs remark-code"><strong>cols</strong> <- ~ Height + Volume

flextable(head(trees)) %>%
  theme_box()
</code></pre>

```{r, echo = FALSE}
cols <- ~ Height + Volume

head(trees, 5) %>% flextable() %>% theme_box()
```

]

]

---

## Selectors


.row[

.col-xs-6[

.marker-writting[
You can select row(s), column(s) or cell(s) of any part to modify its :

* content
* layout
* format

]
]
]

.row[

.col-xs-6[

<pre>
<code class="r hljs remark-code"><strong>cols</strong> <- ~ Height + Volume

flextable(head(trees)) %>%
  theme_box() %>%
  bg(bg = "#475f77", <strong>j = cols</strong>) %>%
  color(color = "white", <strong>j = cols</strong>)
</code></pre>

```{r, echo = FALSE}
cols <- ~ Height + Volume

head(trees, 5) %>% flextable() %>% theme_box() %>%
  bg(bg = "#475f77", j = cols) %>%
  color(color = "white", j = cols)
```

]

]

---

## Selectors


.row[

.col-xs-6[

.marker-writting[
You can select row(s), column(s) or cell(s) of any part to modify its :

* content
* layout
* format

]
]

.col-xs-6[

.marker-writting[
Any function contains parameters `j` and `i`. They can be specified with :

* indices
* formula
* character names

]

]
]

.row[

.col-xs-6[

<pre>
<code class="r hljs remark-code"><strong>cols</strong> <- ~ Height + Volume

flextable(head(trees)) %>%
  theme_box() %>%
  bg(bg = "#475f77", <strong>j = cols</strong>) %>%
  color(color = "white", <strong>j = cols</strong>)
</code></pre>

```{r, echo = FALSE}
cols <- ~ Height + Volume

head(trees, 5) %>% flextable() %>% theme_box() %>%
  bg(bg = "#475f77", j = cols) %>%
  color(color = "white", j = cols)
```

]

]

---

## Selectors


.row[

.col-xs-6[

.marker-writting[
You can select row(s), column(s) or cell(s) of any part to modify its :

* content
* layout
* format

]
]

.col-xs-6[

.marker-writting[
Any function contains parameters `j` and `i`. They can be specified with :

* indices
* formula
* character names

]

]
]

.row[

.col-xs-6[

<pre>
<code class="r hljs remark-code"><strong>cols</strong> <- ~ Height + Volume

flextable(head(trees)) %>%
  theme_box() %>%
  bg(bg = "#475f77", <strong>j = cols</strong>) %>%
  color(color = "white", <strong>j = cols</strong>)
</code></pre>

```{r, echo = FALSE}
cols <- ~ Height + Volume

head(trees, 5) %>% flextable() %>% theme_box() %>%
  bg(bg = "#475f77", j = cols) %>%
  color(color = "white", j = cols)
```

]

.col-xs-6[

<pre>
<code class="r hljs remark-code"><strong>rows</strong> <- ~ Height > 67 & Volume < 19

flextable(head(trees)) %>% 
  theme_box()
</code></pre>

```{r, echo = FALSE}
rows <- ~ Height > 67 & Volume < 19

head(trees, 5) %>% flextable() %>% theme_box()
```

]
]

---

## Selectors


.row[

.col-xs-6[

.marker-writting[
You can select row(s), column(s) or cell(s) of any part to modify its :

* content
* layout
* format

]
]

.col-xs-6[

.marker-writting[
Any function contains parameters `j` and `i`. They can be specified with :

* indices
* formula
* character names

]

]

]

.row[

.col-xs-6[

<pre>
<code class="r hljs remark-code"><strong>cols</strong> <- ~ Height + Volume

flextable(head(trees)) %>%
  theme_box() %>%
  bg(bg = "#475f77", <strong>j = cols</strong>) %>%
  color(color = "white", <strong>j = cols</strong>)
</code></pre>

```{r, echo = FALSE}
cols <- ~ Height + Volume

head(trees, 5) %>% flextable() %>% theme_box() %>%
  bg(bg = "#475f77", j = cols) %>%
  color(color = "white", j = cols)
```

]

.col-xs-6[

<pre>
<code class="r hljs remark-code"><strong>rows</strong> <- ~ Height > 67 & Volume < 19

flextable(head(trees)) %>% 
  theme_box() %>%
  bg(bg = "#475f77", <strong>i = rows</strong>) %>%
  color(color = "white", <strong>i = rows</strong>)
</code></pre>

```{r, echo = FALSE}
rows <- ~ Height > 67 & Volume < 19

head(trees, 5) %>% flextable() %>% theme_box() %>%
  bg(bg = "#475f77", i = rows) %>%
  color(color = "white", i = rows)
```

]
]


---

## Selectors


.row[

.col-xs-6[

.marker-writting[
You can select row(s), column(s) or cell(s) of any part to modify its :

* content
* layout
* format

]
]


.col-xs-6[

.marker-writting[
Any function contains parameters `j` and `i`. They can be specified with :

* indices
* formula
* character names

]
]
]

.row[

.col-xs-6[

<pre>
<code class="r hljs remark-code"><strong>cols</strong> <- ~ Height + Volume

flextable(head(trees)) %>%
  theme_box() %>%
  bg(bg = "#475f77", <strong>j = cols</strong>) %>%
  color(color = "white", <strong>j = cols</strong>)
</code></pre>

```{r, echo = FALSE}
cols <- ~ Height + Volume

head(trees, 5) %>% flextable() %>% theme_box() %>%
  bg(bg = "#475f77", j = cols) %>%
  color(color = "white", j = cols)
```


]


.col-xs-6[

<pre>
<code class="r hljs remark-code"><strong>rows</strong> <- ~ Height > 67 & Volume < 19

flextable(head(trees)) %>% 
  theme_box() %>%
  bg(bg = "#475f77", <strong>i = rows</strong>) %>%
  color(color = "white", <strong>i = rows</strong>)
</code></pre>

```{r, echo = FALSE}
rows <- ~ Height > 67 & Volume < 19

head(trees, 5) %>% flextable() %>% theme_box() %>%
  bg(bg = "#475f77", i = rows) %>%
  color(color = "white", i = rows)
```

]

]

.note-writting[
NB: You can use `%>%` to combine multiple statement
]
